Think deep for reef resilience

### 2025-09-15 paper/paper_draft.qmd
Remove outlier connectivity reefs from post-hoc data analyses

A Quality Assessment and Control process identified reefs with potential data limitations:
reefs with no overlapping bathymetry data, reefs with minimum depth values above sea level
(indicating potential data artifacts), and reefs where bathymetry pixels covered less than
5% of the reef polygon area. This process removed 842 reefs, or 22%, from the initial set of
3806 reefs. Furthermore, reefs that are not associated with GBRMPA Management areas
[@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were also removed from the investigation.
Bioregions which contained fewer than three reefs after these processes were also excluded.
As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining for the
purpose of this investigation. All depth values were converted to positive values (depths
below sea level). The median depth was used to provide an indicative depth value for each
reef. Further limitations are outlined in the Discussion. Code to extract depth estimates,
and the resulting depth estimates themselves, are available at [@iwanaga2025].

![Map of the Great Barrier Reef region, including GBRMPA Management areas (polygons) and all
considered reefs (points). Colour-coded polygons outline GBR marine park management regions,
where orange represents the Far Northern management region, green represents
Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn
[@GBRMPA2007]. Reef centroids are marked individually for visual clarity and are coloured
according to its bioregion [@GBRMPA2024]. All 2429 reefs included in this investigation are
represented in this figure. Annotations represent major coastal settlements along the
GBR.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}

@@

DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the 12-week
rolling sum of HotSpot SST Anomaly values that are greater than 1°C, expressed in units of
°C-weeks. The 12-week accumulation period reflects the cumulative nature of coral thermal
stress. Brief temperature spikes may be tolerable, but sustained or repeated exposure to
elevated temperatures causes progressively greater physiological stress and bleaching
severity. DHW values integrate both the magnitude and duration of thermal stress: a moderate
anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a severe anomaly
(e.g., 3°C) lasting 4 weeks, though the biological impacts may differ. DHW estimates for
each indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for
all pixels touching each reef outline. The process described here was conducted for all 2429
reefs to create DHW projections spanning from 2025 to 2075. Code used to calculate DHW data
and perform analyses involved in this investigation can be found at Grier and Iwanaga
[-@grier2025].

@@

Partial Dependence Analysis was conducted to understand the relationship between features
and bioregion-scale time series cluster predictions using a trained Random Forest (RF)
classifier [@friedman2001]. The analysis utilised the reef characteristics of interest as
the predictors, including the median reef depth, mean DHW for the given GCM, log10-weighted
incoming connectivity, log10-weighted outgoing connectivity, and log10-outgoing-to-incoming
connectivity ratio. The full dataset consisted of the time series cluster assignment of each
of the 2429 reefs under the five GCMs explored, for a total of 12,145 samples. The dataset
was randomly split into training (60%) and testing (40%) subsets to ensure model
generalisability. The RF classifier achieved 79% accuracy on the training set and 59% on the
test set.

@@

Comparing across GCMs, it is common for reefs to switch between clusters, including from Low
to High and vice versa (@sfig-gcm-bioregion-cluster-assignment). Of 2429 reefs, 20% (503) of
reefs have consistent cluster assignment across all GCMs. Of the 503 consistently assigned
reefs, 49% are within the Far Northern Management area, with 7%, 13% and 31% occurring in
the Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management areas
respectively (@sfig-gcm-cluster-map). Of the 503 consistently assigned reefs, 32%, 7% and
61% are clustered into Low, Medium and High clusters respectively. High levels of assignment
variability across GCMs are expected as due to spatial differences in each given GCM’s DHW
trajectories.

@@

Current reef restoration and intervention efforts on the GBR, such as deployment of coral
seeding, coral fragment devices and Crown of Thorns Starfish control, target reefs with
sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are
no explicit justifications for this depth range, intervention depth is likely constrained by
snorkelling and diving deployment and monitoring logistical accessibility, visual
identification of sites from the surface, in combination with tourism return value. Our
results suggest that of the assessed reefs occurring within the 1-10m depth range (1736
reefs), 57% (991) of reefs are consistently clustered into the Low and Medium cover clusters
across the GCMs (at the GBRMPA management region scale), with many unable to maintain
positive carbonate budgets under future conditions. Partial dependence analysis revealed a
range of depths from 10-15m where the probability of a reef being clustered into the High
cover cluster increased substantially. Additionally, two-way partial dependence analysis
revealed that high incoming connectivity is important for High cluster assignment for reefs
at depths of \>10m. Considering this 10-15m depth range when assessing possible intervention
sites may reduce the exposure of planted and seeded corals to high thermal stress, while
still maintaining effective logistical access to sites. Managers are also likely to consider
the potential for positive flow on effects due to outgoing connectivity when selecting
intervention sites [@hock2017]. Two-way partial dependence analysis revealed reefs with high
depths and high outgoing connectivity levels have a high probability of being clustered into
more resilient reef clusters (@sfig-ts-cluster-pdp-twoway-outgoing). These results suggest
that interventions targetting deep reefs will also benefit from high incoming and outgoing
connectivity levels, allowing for high potential for site resilience and outgoing flow of
benefits and recovery. Transient, and difficult to measure, properties such as reef
connectivity are likely to increase uncertainty in intervention planning to a greater degree
than environmental characteristics such as reef depth. Overall, reef intervention planning
is a complex and challenging decision-making process [@anthony2020], and our results suggest
that intervention site depth may be an important factor to additionally consider when
assessing the long-term resilience of sites.

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by management area scale cluster assignment.
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Reefs that do not have a consistent cluster
assignment level across all GCMs at mangement area scale are coloured grey. All consistently
clustered reefs are coloured according to their management area scale cluster assignment.
Green represents reefs in the low cover cluster, orange represents reefs in the medium cover
cluster and blue represents reefs in the high cover cluster. All 2429 reefs included in this
investigation are represented in this figure. Annotations represent major coastal
settlements along the GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
fig-align="center" width="14.82cm"}

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by median reef depth. Colour-coded areas outline GBR
marine park management regions, where orange represents the Far Northern management region,
green represents Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers
Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for visual clarity.
Darker colours represent greater reef depth values than lighter colours. All 2429 reefs
included in this investigation are represented in this figure. Annotations represent major
coastal settlements along the GBR.](../figs/depth_med_input_map.png){#sfig-depth-map
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by reef carrying capacity (coral habitable area).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Darker colours represent greater carrying capacity
area values than lighter colours. All 2429 reefs included in this investigation are
represented in this figure. Annotations represent major coastal settlements along the
GBR.](../figs/abs_k_area_input_map.png){#sfig-abs-k-area-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by outgoing connection strength (Log10). Colour-coded
areas outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Darker colours represent higher outgoing connection strength values than
lighter colours. All 2429 reefs included in this investigation are represented in this
figure. Annotations represent major coastal settlements along the
GBR.](../figs/log_out_strength_input_map.png){#sfig-outgoing-conn-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by source-to-sink connectivity ratio (Log10).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Darker colours represent higher source-to-sink
values than lighter colours. Source-to-sink ratio values above zero (one on normal scale)
indicate a reef has greater outgoing than incoming connectivity. All 2429 reefs included in
this investigation are represented in this figure. Annotations represent major coastal
settlements along the GBR.](../figs/log_so_to_si_input_map.png){#sfig-sotosi-conn-map
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by larval retention probability (Log10). Colour-coded
areas outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Darker colours represent higher probability of retaining spawned larvae than
lighter colours. All 2429 reefs included in this investigation are represented in this
figure. Annotations represent major coastal settlements along the
GBR.](../figs/log_self_strength_input_map.png){#sfig-self-conn-map fig-align="center"
width="14.82cm"}

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by median number of years exceeding positive carbonate
budget threshold. Colour-coded areas outline GBR marine park management regions, where
orange represents the Far Northern management region, green represents Cairns/Cooktown, red
covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids
are marked individually for visual clarity. Reefs that have a median positive carbonate
budget year value of 0 years are coloured in grey. All other reefs are coloured according to
their median years across threshold values, with darker colours representing greater number
of years with positive carbonate budgets than lighter colours. All 2429 reefs included in
this investigation are represented in this figure. This map depicts values from the
ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/median_carbonate_budget_map.png){#sfig-carb-budget-map
fig-align="center" width="14.82cm"}

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by mean time series DHW value. Colour-coded areas
outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Darker colours represent higher mean DHW values than lighter colours. All
2429 reefs included in this investigation are represented in this figure. This map depicts
values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/mean_dhw_input_map.png){#sfig-mean-dhw-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by weighted incoming connectivity levels (Log10).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Darker colours represent higher weighted incoming
connectivity values than lighter colours. All 2429 reefs included in this investigation are
represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations
represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/weighted_incoming_conn_input_map.png){#sfig-incoming-conn-map
fig-align="center" width="14.82cm"}

>>>>

A Quality Assessment and Control process identified reefs with potential data limitations:
reefs with no overlapping bathymetry data, reefs with minimum depth values above sea level
(indicating potential data artifacts), and reefs where bathymetry pixels covered less than
5% of the reef polygon area. This process removed 842 reefs, or 22%, from the initial set of
3806 reefs. Furthermore, reefs that are not associated with GBRMPA Management areas
[@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were also removed from the investigation.
Bioregions which contained fewer than three reefs after these processes were also excluded.
As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining. All depth
values were converted to positive values (depths
below sea level). The median depth was used to provide an indicative depth value for each
reef. Further limitations are outlined in the Discussion. Code to extract depth estimates,
and the resulting depth estimates themselves, are available at [@iwanaga2025]. To ensure
effective data analysis, reefs with incoming or outgoing connectivity values below the 5th
percentile were removed from post-hoc analyses, leaving 2197 reefs remaining for display in results.

![Map of the Great Barrier Reef region, including GBRMPA Management areas (polygons) and all
considered reefs (points). Colour-coded polygons outline GBR marine park management regions,
where orange represents the Far Northern management region, green represents
Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn
[@GBRMPA2007]. Reef centroids are marked individually for visual clarity and are coloured
according to its bioregion [@GBRMPA2024]. All 2197 reefs included in this investigation are
represented in this figure. Annotations represent major coastal settlements along the
GBR.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}

@@

DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the 12-week
rolling sum of HotSpot SST Anomaly values that are greater than 1°C, expressed in units of
°C-weeks. The 12-week accumulation period reflects the cumulative nature of coral thermal
stress. Brief temperature spikes may be tolerable, but sustained or repeated exposure to
elevated temperatures causes progressively greater physiological stress and bleaching
severity. DHW values integrate both the magnitude and duration of thermal stress: a moderate
anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a severe anomaly
(e.g., 3°C) lasting 4 weeks, though the biological impacts may differ. DHW estimates for
each indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for
all pixels touching each reef outline. The process described here was conducted for all 2197
reefs to create DHW projections spanning from 2025 to 2075. Code used to calculate DHW data
and perform analyses involved in this investigation can be found at Grier and Iwanaga
[-@grier2025].

@@

Partial Dependence Analysis was conducted to understand the relationship between features
and bioregion-scale time series cluster predictions using a trained Random Forest (RF)
classifier [@friedman2001]. The analysis utilised the reef characteristics of interest as
the predictors, including the median reef depth, mean DHW for the given GCM, log10-weighted
incoming connectivity, log10-weighted outgoing connectivity, and log10-outgoing-to-incoming
connectivity ratio. The full dataset consisted of the time series cluster assignment of each
of the 2197 reefs under the five GCMs explored, for a total of 12,145 samples. The dataset **[]
was randomly split into training (60%) and testing (40%) subsets to ensure model
generalisability. The RF classifier achieved 79% accuracy on the training set and 59% on the
test set.

@@

Comparing across GCMs, it is common for reefs to switch between clusters, including from Low
to High and vice versa (@sfig-gcm-bioregion-cluster-assignment). Of 2197 reefs, 21% (462) of
reefs have consistent cluster assignment across all GCMs. Of the 462 consistently assigned
reefs, 23% are within the Far Northern Management area, with 1%, 55% and 21% occurring in
the Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management areas
respectively (@sfig-gcm-cluster-map). Of the 462 consistently assigned reefs, 34%, 18% and
47% are clustered into Low, Medium and High clusters respectively. High levels of assignment
variability across GCMs are expected as due to spatial differences in each given GCM’s DHW
trajectories.

@@

Current reef restoration and intervention efforts on the GBR, such as deployment of coral
seeding, coral fragment devices and Crown of Thorns Starfish control, target reefs with
sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are
no explicit justifications for this depth range, intervention depth is likely constrained by
snorkelling and diving deployment and monitoring logistical accessibility, visual
identification of sites from the surface, in combination with tourism return value. Our
results suggest that of the assessed reefs occurring within the 1-10m depth range (1551
reefs), 59% (920) of reefs are consistently clustered into the Low and Medium cover clusters
across the GCMs (at the GBRMPA management region scale), with many unable to maintain
positive carbonate budgets under future conditions. Partial dependence analysis revealed a
range of depths from 10-15m where the probability of a reef being clustered into the High
cover cluster increased substantially. Additionally, two-way partial dependence analysis
revealed that high incoming connectivity is important for High cluster assignment for reefs
at depths of \>10m. Considering this 10-15m depth range when assessing possible intervention
sites may reduce the exposure of planted and seeded corals to high thermal stress, while
still maintaining effective logistical access to sites. Managers are also likely to consider
the potential for positive flow on effects due to outgoing connectivity when selecting
intervention sites [@hock2017]. Two-way partial dependence analysis revealed reefs with high
depths and high outgoing connectivity levels have a high probability of being clustered into
more resilient reef clusters (@sfig-ts-cluster-pdp-twoway-outgoing). These results suggest
that interventions targetting deep reefs will also benefit from high incoming and outgoing
connectivity levels, allowing for high potential for site resilience and outgoing flow of
benefits and recovery. Transient, and difficult to measure, properties such as reef
connectivity are likely to increase uncertainty in intervention planning to a greater degree
than environmental characteristics such as reef depth. Overall, reef intervention planning
is a complex and challenging decision-making process [@anthony2020], and our results suggest
that intervention site depth may be an important factor to additionally consider when
assessing the long-term resilience of sites.

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by management area scale cluster assignment.
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Reefs that do not have a consistent cluster
assignment level across all GCMs at mangement area scale are coloured grey. All consistently
clustered reefs are coloured according to their management area scale cluster assignment.
Green represents reefs in the low cover cluster, orange represents reefs in the medium cover
cluster and blue represents reefs in the high cover cluster. All 2197 reefs included in this
investigation are represented in this figure. Annotations represent major coastal
settlements along the GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
fig-align="center" width="14.82cm"}

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by median reef depth. Colour-coded areas outline GBR
marine park management regions, where orange represents the Far Northern management region,
green represents Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers
Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for visual clarity.
Darker colours represent greater reef depth values than lighter colours. All 2197 reefs
included in this investigation are represented in this figure. Annotations represent major
coastal settlements along the GBR.](../figs/depth_med_input_map.png){#sfig-depth-map
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by reef carrying capacity (coral habitable area).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Darker colours represent greater carrying capacity
area values than lighter colours. All 2197 reefs included in this investigation are
represented in this figure. Annotations represent major coastal settlements along the
GBR.](../figs/abs_k_area_input_map.png){#sfig-abs-k-area-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by outgoing connection strength (Log10). Colour-coded
areas outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Darker colours represent higher outgoing connection strength values than
lighter colours. All 2197 reefs included in this investigation are represented in this
figure. Annotations represent major coastal settlements along the
GBR.](../figs/log_out_strength_input_map.png){#sfig-outgoing-conn-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by source-to-sink connectivity ratio (Log10).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Darker colours represent higher source-to-sink
values than lighter colours. Source-to-sink ratio values above zero (one on normal scale)
indicate a reef has greater outgoing than incoming connectivity. All 2197 reefs included in
this investigation are represented in this figure. Annotations represent major coastal
settlements along the GBR.](../figs/log_so_to_si_input_map.png){#sfig-sotosi-conn-map
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by larval retention probability (Log10). Colour-coded
areas outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Darker colours represent higher probability of retaining spawned larvae than
lighter colours. All 2197 reefs included in this investigation are represented in this
figure. Annotations represent major coastal settlements along the
GBR.](../figs/log_self_strength_input_map.png){#sfig-self-conn-map fig-align="center"
width="14.82cm"}

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by median number of years exceeding positive carbonate
budget threshold. Colour-coded areas outline GBR marine park management regions, where
orange represents the Far Northern management region, green represents Cairns/Cooktown, red
covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids
are marked individually for visual clarity. Reefs that have a median positive carbonate
budget year value of 0 years are coloured in grey. All other reefs are coloured according to
their median years across threshold values, with darker colours representing greater number
of years with positive carbonate budgets than lighter colours. All 2197 reefs included in
this investigation are represented in this figure. This map depicts values from the
ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/median_carbonate_budget_map.png){#sfig-carb-budget-map
fig-align="center" width="14.82cm"}

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by mean time series DHW value. Colour-coded areas
outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Darker colours represent higher mean DHW values than lighter colours. All
2197 reefs included in this investigation are represented in this figure. This map depicts
values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/mean_dhw_input_map.png){#sfig-mean-dhw-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by weighted incoming connectivity levels (Log10).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Darker colours represent higher weighted incoming
connectivity values than lighter colours. All 2197 reefs included in this investigation are
represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations
represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/weighted_incoming_conn_input_map.png){#sfig-incoming-conn-map
fig-align="center" width="14.82cm"}
